Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs

### 2014-12-04 doc/GMP2015/s01_introduction.tex
s01_introduction.tex edited online with Bitbucket

\section{Introduction}
Modeling, analysis and design of self-similar, aperiodic layered materials as geometric constraint systems

Many natural and engineered materials are recursively self-similar \cite{Intro1}, 
spanning multiple scales. Within any one scale, the materials are quasiuniform, but aperiodic, 
consisting of a few different motifs repeating in random combinations.
In addition, many materials are stacked two dimensional (2D) layers, where each layer is independently self-similar and aperiodic.
Each layer is not necessarily planar, i.e., it consists of multiple, inter-constraining planar (genus 0) monolayers. 
Furthermore, a layer is often   either isostatic or somewhat flexible, and rarely self-stressed, at any scale. This is 
consistent with a self-assembled structure that minimizes mass, optimally distributes external stresses and itself 
participates in the assembly of diverse, 
larger structures with multiple functions, all within the same layer.

@@

It is natural to model such a self-similar, aperiodic material using appropriate geometric primitives under metric or algebraic constraints; design the 
constraint-system to achieve the desired properties; and study robustness/sensitivity to constraint variations.

Two key observations serve as the motivations for this paper:
As constraint systems, the above 2D {\em sesamacs} (Self-similar, aperiodic material constraint systems) involve multiple types of 
well-studied geometric primitives and constraints: they can be modeled as so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid components \cite{XX}.

Recursive decompositions of {\em slamacs} into rigid subsystems is For , is important to understand or design the structural 
and mechanical properties - such as rigidity, flexes and distribution of external stresses within the layer - at all scales.

>>>>

\section{Introduction}
Modeling, analysis and design of self-similar, aperiodic layered materials using geometric constraint systems

Many natural and engineered materials are stacked two dimensional (2D) layers, where the structure within each layer is recursively 
self-similar \cite{Intro1}, 
spanning multiple scales. Within any one scale, the material layer is aperiodic, and quasi-uniform,
consisting of a few repeated motifs appearing in disordered arrangments.
Each layer is not necessarily planar, i.e., it consists of multiple, inter-constraining planar (genus 0) monolayers. 
Furthermore, a layer is often   either isostatic or somewhat flexible, and rarely self-stressed, at any scale. These properties are
consistent with a self-assembled 2D structure that minimizes mass, optimally distributes external stresses and itself 
participates in the assembly of diverse and multifunctional, 
larger 2D structures.

@@

In order to study structural and mechanical properties such as rigidity, flexes and distribution of external stresses 
within the material layer, 
it is natural to model them using appropriate geometric primitives under metric or algebraic constraints, 
Such  2D {\em sesamacs} (Self-similar, aperiodic material constraint systems) can be used to 
study robustness/sensitivity to constraint variations and to design material layers 
to achieve the desired properties.

Two key observations serve as the motivations for this paper:
As constraint systems, 2D sesamacs involve multiple types of 
well-studied geometric constraint systems: so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid components \cite{XX}.

Recursive decompositions of 2D sesamacs into rigid subsystems is important in order to understand or design rigidity, flexes and distribution 
of external stresses  -- at all scales.
